A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
improvements of "Southeastern Central Europe"

`r a("Southeastern Central Europe")`^[Amount of graves in Radon-B for this region.]:
The artificial study region *Southeastern Central Europe* comprises the eastern part of Austria (Upper Austria, Lower Austria, Styria, Burgenland), the northwest of Hungary, western Slovakia, Moravia and large parts of Bohemia. The density of ^14^C data on graves from radon B is low -- individual data are available from the various regions, but large areas must manage without evidence. Diachronic, the data volume is consistently low and reaches a low point in the Middle Bronze Age. While for the *burial type* variable a constant flow of information is given, the number of graves without information on *burial construction* increases in the Late Bronze Age to such an extent that no statement at all can be derived for them. To assess the relative development within the variables *burial type* and *burial construction*, as predicted with the Radon-B data set on the basis of ^14^C data, a résumé must first be drawn from the data in chapter \@ref(regions-archaeological-overview). This is complicated by the fact that the region intersects diverse geographical and cultural areas. In the southeast of Central Europe, cremation and bodily burial already existed side by side in the Early Bronze Age, and the local tradition remained stable in this respect also due to the expansion of the burial mound tradition in the Middle Bronze Age -- with a slight overall increase in cremation graves. The Urnfield period brought the transition to the absolute dominance of cremation burial. The development of the *burial type* variable in the Radon-B proxy shows this development correctly. The information from ^14^C data on *burial construction* correctly traces the relevance of flat burials in the Early Bronze Age, but the latter are then overemphasized in the Middle Bronze Age compared to the construction of burial mounds. In the Late Bronze Age, burials on flat burial grounds were frequent, although hills of the burial mound culture were also further documented. This circumstance -- certainly due to the small amount of data -- cannot be correctly deduced from radon-B.

>>>>

General observations: **TODO**

`r a("Southeastern Central Europe")`^[Amount of graves in Radon-B for this region.]:
The artificial study region *Southeastern Central Europe* comprises the eastern part of Austria (Upper Austria, Lower Austria, Styria, Burgenland), the northwest of Hungary, Western Slovakia, Moravia and large parts of Bohemia (Figure \ref{map} B). The density of ^14^C data on graves in Radon-B is low -- individual dates are available from the various regions, but large areas are without evidence. Diachronically the amount of data is consistently low and reaches a minimum in the Middle Bronze Age. While for the *burial type* variable a constant flow of information is given, the number of graves without information on *burial construction* increases in the Late Bronze Age to such an extent that no meaningful overview can be derived. The comparison with archaeological observations is complicated by the fact that the region intersects diverse geographical and cultural areas. In the southeast of Central Europe, cremation and bodily burial already existed side by side in the Early Bronze Age, and the local tradition remained stable in this respect also due to the expansion of the burial mound tradition in the Middle Bronze Age -- with a slight overall increase in cremation graves. The Urnfield period brought the transition to the absolute dominance of cremation burial. The development of the *burial type* variable in the Radon-B proxy shows this development correctly. The information from ^14^C data on *burial construction* correctly traces the relevance of flat burials in the Early Bronze Age, but the latter are then overemphasized in the Middle Bronze Age compared to the construction of burial mounds. In the Late Bronze Age, burials on flat burial grounds were frequent, although burial mounds of the Tumulus Culture were also further documented. This impact cannot be correctly deduced from Radon-B -- certainly due to the small amount of data.
